Reproducibility in Plant Pathology

### 2018-01-10 README.rmd
Add Sydney to list of authors in Readme and format e-mail links
Fix links to pkgdown site

[![Travis-CI Build Status](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/phytopathology/Reproducibility_in_Plant_Pathology)

@@

For optimal webviewing of this report, please see the [HTML version](http://htmlpreview.github.io/?https://github.com/phytopathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).

@@

The files at the URL above will generate the results as found in the publication. The files hosted at https://github.com/phytopathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.

@@

Adam H Sparks (adamhsparks@gmail.com)

Emerson M Del Ponte (delponte@ufv.br)

Zachary Foster (zacharyfoster1989@gmail.com)

Niklaus J Grünwald (grunwaln@science.oregonstate.edu)

@@

```
git clone https://github.com/phytopathology/Reproducibility_in_Plant_Pathology.git
```

@@

    docker run -dp 8787:8787 phytopathology/Reproducibility_in_Plant_Pathology

>>>>

[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology.svg?branch=master)](https://travis-ci.org/openplantpathology/Reproducibility_in_Plant_Pathology)

@@

For optimal webviewing of this report, please see the [HTML version](http://htmlpreview.github.io/?https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology/blob/master/inst/paper/Sparks_et_al-main_text.html).

@@

The files at the URL above will generate the results as found in the publication. The files hosted at https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology are the development versions and may have changed since the report was published.

@@

Adam H Sparks (<adamhsparks@gmail.com>)

Emerson M Del Ponte (<delponte@ufv.br>)

Sydney Everhart (<everhart@unl.edu>)

Zachary Foster (<zacharyfoster1989@gmail.com>)

Niklaus J Grünwald (<grunwaln@science.oregonstate.edu>)

@@

```
git clone https://github.com/openplantpathology/Reproducibility_in_Plant_Pathology.git
```

@@

    docker run -dp 8787:8787 openplantpathology/Reproducibility_in_Plant_Pathology
